Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-02-24 paper.tex
FastR pipeline description

\begin{document}
\title{Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data}
\author{Valerie Hayot-Sasson}
\maketitle
\begin{abstract}
  Text of abstract.  
\end{abstract}
\tableofcontents
\chapter{Introduction}
intro here
\chapter{BigData and Open science in neuroimaging}
    \note{Likely will not be split in two separate sections}
    \section{large images}
        \begin{itemize}  
            \item BigBrain
            \item Micro CT 
            \item EM 
        \end{itemize}
    \section{large datasets}
    	\note{off the top of my head, but need to double check}
        \begin{itemize}
            \item HCP
            \item ADNI
            \item OpenFMRI
            \item BIDS/BIDS apps
        \end{itemize}
    An effective engine to process such data requires the following characteristics
        \begin{itemize}
            \item in-memory computing
            \item data locality
            \item lazy evaluation
        \end{itemize}
        \section{open-science /data sharing platforms for neuroimaging}
        		is open science just data sharing, computing. 
        		\subsection{Introduction}
		\subsection{CBRAIN}
		\subsection{OpenNEURO}
		\subsection{NeuroData}
\chapter{Workflow engines for neuroimaging data}
	\section{Definition of workflows/pipelines}

@@

        \subsection{limitations of SPM}
    \section{Nextflow}
        \subsection{summary}
        Nextflow is a POSIX-compatible pipeline engine for scientific workflows.
It extends the Groovy programming language to provide an  intuitive domain-specific language (DSL) 
that enables users to easily describe their workflows. Unlike pipeline engines such as Nipype and
PSOM, Netflow does not employ DAG. It instead adheres to the
\textit{Dataflow} programming model which decides how data will flow through the pipeline at
runtime \note{fix this sentence}. Nextflow prides itself on allowing the
integration of containerized tools to address the issue of numerical stability
that may arise from different environment setups.

@@

The \textit{Interface} class is responsible for executing a call to the command line tool.
It dictates the tags that must be defined within the interface tag of the
\textit{Tool}. For instance, the generic interface class requires details on the
input and output's id, cardinality (number of input values) and DataType (a
python object denoting the details of the Input or Output's data type).
Verification is done by FastR to determine if the linked Input and Output data
types are compatible \note{data types can also be grouped, but did not really
understand that}.

In FastR, there are four types of \textit{Nodes}: normal Nodes, Sink Nodes,
Source Nodes and Constant Nodes. Data enters the network through Source or
Constant Nodes and exit through Sink Nodes. Constant nodes differ from Source
Nodes in that their input data are defined by the network \note{Not sure if
saying this correctly}. Normal nodes are responsible for processing the
data. Nodes are connected to each other through links that highlight the
dependencies and form the \textit{Network}. Once the \textit{Netwokr} is
defined, it can be executed.

        \subsection{Pipeline execution}
        \subsection{Debugging and Provenance}
    \section{OpenMOLE}
        \subsection{summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and Provenance}
    \section{LONI}
    \section{Automatic Analysis}
    \section{Dipy, Make, Pydiper} 
    \section{Use of containers in Workflow engines} 
        \subsection{use of containers in nipype, psom, spm}

>>>>

\begin{document}
\title{Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data}
\author{Valerie Hayot-Sasson}
\maketitle
\begin{abstract}
  Text of abstract.  
\end{abstract}
\tableofcontents
\chapter{Introduction}
intro here -mention hpc, data centre, cloud. 
\chapter{BigData and Open science in neuroimaging}
    \note{Likely will not be split in two separate sections}
    \section{large images}
        \begin{itemize}  
            \item BigBrain
            \item Micro CT 
            \item EM 
        \end{itemize}
    \section{large datasets}
    	\note{off the top of my head, but need to double check}
        \begin{itemize}
            \item HCP
            \item ADNI
            \item OpenFMRI
            \item BIDS/BIDS apps
        \end{itemize}
    An effective engine to process such data requires the following characteristics
        \begin{itemize}
            \item in-memory computing
            \item data locality
            \item lazy evaluation
        \end{itemize}
        \section{open-science /data sharing platforms for neuroimaging}
        		is open science just data sharing, computing. 
        		\subsection{Introduction}
		\subsection{CBRAIN}
		\subsection{OpenNEURO}
		\subsection{NeuroData}
\chapter{Workflow engines for neuroimaging data}
	\section{Definition of workflows/pipelines}

@@

        \subsection{limitations of SPM}
    \section{Nextflow}
        \subsection{summary}
        Nextflow is a POSIX-compatible pipeline engine for scientific workflows.
It extends the Groovy programming language to provide an  intuitive domain-specific language (DSL) 
that enables users to easily describe their workflows. Unlike pipeline engines such as Nipype and
PSOM, Netflow does not employ DAG. It instead adheres to the
\textit{Dataflow} programming model which decides how data will flow through the pipeline at
runtime \note{fix this sentence}. Nextflow prides itself on allowing the
integration of containerized tools to address the issue of numerical instability
that may arise from different environment setups.

@@

The \textit{Interface} class is responsible for executing a call to the command line tool.
It dictates the tags that must be defined within the interface tag of the
\textit{Tool}. For instance, the generic interface class requires details on the
input and output's id, cardinality (number of input values) and DataType (a
python object denoting the details of the Input or Output's data type).
DataTypes can also be grouped, allowing an inputs containing various files types
to be inputted to applications which can support the file types.
Verification is done by FastR to determine if the linked Input and Output data
types are compatible.

Input samples can consist of one or more values, in which the output is also a
sample consisting of the same number of values. During the instances in which it
is desirable to apply the same task to multiple inputs, a multidimensional array of samples, known as a collection, can be supplied to a
\textit{Node} for processing. If there are multiple input samples, they can be
passed to a node in pairwise behaviour (e.g. 1-1) or cross-product behaviour
(e.g. nxn) \textit{need to better explain this}.

Output samples may need to be expanded (i.e. a single sample of values becomes separate
samples) or collapsed (i.e. multiple samples become a single sample of values).
FastR provides data link flow directives for such operations.

In FastR, there are four types of \textit{Nodes}: normal Nodes, Sink Nodes,
Source Nodes and Constant Nodes. Data enters the network through Source or
Constant Nodes and exit through Sink Nodes. Constant nodes differ from Source
Nodes in that their input data are defined by the network \note{Not sure if
saying this correctly}. Normal nodes are responsible for processing the
data. Nodes are connected to each other through links that highlight the
dependencies and form the \textit{Network}. Once the \textit{Network} is
defined, it can be executed.

The data type of the Source Node and Sink Node must be defined in the
\textit{Network} definition.
The data is define at runtime by evaluation of the uniform resource identifier
(URI). Multiple URIs can be defined through the use of wildcards and searches. Plugins are used to read and write data to
different filesystems specified in the URI scheme. Currently, FastR supports
virtual file system (VSF), csv files and XNAT. Plugins to support other
filesystems can easily be added to FastR. In addition, plugins that can only
read, write, or perform searches can also be created.

        \subsection{Pipeline execution}

        \subsection{Debugging and Provenance}
    \section{OpenMOLE}
        \subsection{summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and Provenance}
    \section{LONI}
    \section{Automatic Analysis}
    \section{Dipy, Make, Pydiper} 
    \section{Use of containers in Workflow engines} 
        \subsection{use of containers in nipype, psom, spm}
